Capstone Movielens Report

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  the `model.tune.param_range` function input parameters described.

##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function
\

@@

###### Sugnature
\
```{r eval=FALSE}
model.tune.param_range <- function(loop_starter,
                             tune_dir_path,
                             cache_file_base_name,
                             fn_tune.test.param_value,
                             max.identical.min_RMSE.count = 4,
                             is.cv = TRUE,
                             endpoint.min_diff = 0,
                             break.if_min = TRUE,
                             steps.beyond_min = 2){
  # ...
  list(best_result = param_values.best_result,
       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
       tuned.result = data.frame(parameter.value = parameter.value,
                                 RMSE = result.RMSE))
}
```

@@

####### max.identical.min_RMSE.count
\
If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter. When it is reached, the algorithm considers the task execution to be complete.

#######  
\

  - **is.cv:** ;

#######  
\

  - **endpoint.min_diff:** ;

#######  
\

  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps

#######  
\

specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;

  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.

#######  
\

###### Details
\
During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.

>>>>

##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
\

@@

###### Sugnature
\
```{r eval=FALSE}
model.tune.param_range <- function(loop_starter,
                             tune_dir_path,
                             cache_file_base_name,
                             fn_tune.test.param_value,
                             max.identical.min_RMSE.count = 4,
                             endpoint.min_diff = 0,
                             break.if_min = TRUE,
                             steps.beyond_min = 2){
  # ...
  list(best_result = param_values.best_result,
       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
       tuned.result = data.frame(parameter.value = parameter.value,
                                 RMSE = result.RMSE))
}
```

@@

####### max.identical.min_RMSE.count = 4
\
If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter. When it is reached, the algorithm considers the task execution to be complete.

####### endpoint.min_diff = 0
\
Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the [Details](#func.model.tune.param_range.details) section below).

####### break.if_min = TRUE 
\
This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).

####### steps.beyond_min = 2 
\
This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).

###### Details {#func.model.tune.param_range.details}
\
During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development:  the `model.tune.param_range` function input parameters described.

\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
Function}{model.tune.param\_range Function}}\label{model.tune.param_range-function}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
\NormalTok{                             tune\_dir\_path,}
\NormalTok{                             cache\_file\_base\_name,}
\NormalTok{                             fn\_tune.test.param\_value,}
                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{,}
                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
  \CommentTok{\# ...}
  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

max.identical.min\_RMSE.count

@@

\begin{itemize}
\tightlist
\item
  \textbf{is.cv:} ;
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{endpoint.min\_diff:} ;
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
  whether the function should terminate after completing the number of
  steps
\end{itemize}

specified by the parameter \texttt{steps.beyond\_min}, after the minimum
value of the \texttt{RMSE} has been found;

\begin{itemize}
\tightlist
\item
  \textbf{steps.beyond\_min = 2:} (takes effect only if
  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
  number of steps after finding the minimum value of the \texttt{RMSE},
  upon completion of which the function should terminate.
\end{itemize}

>>>>

\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
Function}{model.tune.param\_range Function}}\label{func.model.tune.param_range}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
\NormalTok{                             tune\_dir\_path,}
\NormalTok{                             cache\_file\_base\_name,}
\NormalTok{                             fn\_tune.test.param\_value,}
                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{,}
                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
  \CommentTok{\# ...}
  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

max.identical.min\_RMSE.count = 4

@@

endpoint.min\_diff = 0

\hfill\break
Defines the sensitivity threshold for determining the neighborhood
boundaries of the minimum \texttt{RMSE} value (for details, see the
\hyperref[func.model.tune.param_range.details]{Details} section below).

break.if\_min = TRUE

\hfill\break
This is a parameter that is required for the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function that is called internally during execution (see the description
of the \texttt{tune.model\_param} function
\hyperref[func.tune.model_param]{above}).

steps.beyond\_min = 2

\hfill\break
This is a parameter that is required for the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function that is called internally during execution (see the description
of the \texttt{tune.model\_param} function
\hyperref[func.tune.model_param]{above}).
